Music Perception 1: Variability Analysis

### 2022-01-14 experiment-1/analysis/prereg_analysis/prereg_analysis.Rmd
merge perception-v1.0 / move stuff to experiment-1
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Stimuli
- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli). The half of them was selected from the teaching condition and the other half was from the performing condition.
  + 24 for teaching-articulation performances
  + 24 for performing-articulation performances
  + 24 for teaching-dynamics performances
  + 24 for performing-dynamics performances

@@

```{r read, include = FALSE}
# read files and combine them
data_ls <- list.files("../data", pattern = "csv")
combined <- lapply(data_ls, function(f){
  fread(paste("../data/", f, sep = ""), sep = ",")
})
all_data <- do.call(rbind.data.frame, combined)

@@

data_box <- data.table(subjectNumber = ind_data_ad$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")
box
```

>>>>

## Stimuli
- Stimuli were selected from the previous study ([the sound of teaching music/experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1)).
- 48 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 96 stimuli). Half of them was selected from the teaching condition and the other half was from the performing condition.
  + 24 for teaching-articulation performances
  + 24 for performing-articulation performances
  + 24 for teaching-dynamics performances
  + 24 for performing-dynamics performances

@@

```{r read, include = FALSE}
# read files and combine them
data_ls <- list.files("../../data", pattern = "csv")
combined <- lapply(data_ls, function(f){
  fread(paste("../../data/", f, sep = ""), sep = ",")
})
all_data <- do.call(rbind.data.frame, combined)

@@

data_box <- data.table(subjectNumber = ind_data_ad[Skill == "articulation"]$subjectNumber, articulation = ind_data_ad[Skill == "articulation"]$Percent, dynamics = ind_data_ad[Skill == "dynamics"]$Percent)
box <- ggpaired(data_box, cond1 = "articulation", cond2 = "dynamics", line.color = "gray", line.size = 0.4, ylab = "Correct %")
box
```

### 2022-01-14 experiment-1/analysis/questionnaire.Rmd
merge perception-v1.0 / move stuff to experiment-1
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Music Perception 2: Questionnaire"
output: html_notebook
---

@@

# extract the total number of years of training for the longest instrument (input manually based on the original csv file)
dt$Training <- c(14, 13, 7, 18, 23, 12, 17, 20, 12, 7, 12, 7, 7, 13, 20, 15, 6)

# exclude participants
dt_included <- dt[SubNr != 4]

>>>>

---
title: "Music Perception 1: Questionnaire"
output: html_notebook
---

@@

# extract the total number of years of training for the longest instrument (input manually based on the original csv file)
dt$Training <- c(7, 7, 10, 6, 7, 6, 6, 20, 12, 7, 7, 11, 9, 16, 20, 15, 19, 14, 24, 12, 14)

# exclude participants
dt_included <- dt[SubNr != 9]

### 2022-01-14 experiment-1/analysis/variability.Rmd
merge perception-v1.0 / move stuff to experiment-1
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

ggline(a_p_6[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_ (Staccato)") +
  scale_x_continuous(breaks = seq(1,66,1))

>>>>

ggline(a_p_6[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_6 (Staccato)") +
  scale_x_continuous(breaks = seq(1,66,1))
